Interactive Markdown to explore Clustering

### 2017-07-04 src/ClusterComparison.Rmd
updates

clustDat <- readRDS("../data/Robjects/secondRun_2500/ClusterComparison.rds") 
# bootDat <- readRDS("../data/Robjects/ClusterBootstrap.rds")
dataList <- readRDS("../data/Robjects/secondRun_2500/ExpressionList_QC_norm.rds")
set.seed(300)
dataList <- subSample(dataList,cell.number=1000)

@@

#Gene and Cell filtering
m <- m[fD$keep,pD$PassAll]
pD <- pD[pD$PassAll,]
fD <- fD[fD$keep,]
#Normalization
m <- t(t(m)/pD$sf)

@@

@@

#Visualize Dendrograms
clustering <- reactive({
    lbl <- paste(input$dm,input$lk,input$ds,sep="_")
    cluss <- clustDat[[lbl]][["Labels"]]
})

@@

# renderPlot({
#     clust <- clustering()
#     pD$cluster <- clust
#     nclust <- length(unique(clust))
#     ord <- arrange(pD, cluster) 
#     simMat <- asSim(clust$dis)
#     simMat.ord <- as.matrix(simMat)[as.character(ord$barcode),
#                                     as.character(ord$barcode)]
#     library(pheatmap)
#     annoCol <- data.frame("cluster"=as.factor(ord$cluster),
#                           "Condition"=ord$Condition)
#     rownames(annoCol) <- as.character(ord$barcode)
#     ann_colors <- list("cluster"=rainbow(nclust))
#     names(ann_colors$cluster) <- c(min(ord$cluster):max(ord$cluster))
#     pheatmap(simMat.ord,
#              cluster_rows=FALSE,
#              cluster_cols=FALSE,
#              show_rownames=FALSE,
#              show_colnames=FALSE,
#              annotation_col=annoCol,
#              annotation_colors=ann_colors)
# }, width=1200, height=1200)

renderPlot({
    pD$cluster <- clustering()
    genes <- c("Acta2","Csn3","Epcam","Krt8")
	 plotGeneDist(m, pD, fD, genes, colorBy="cluster")
   }, width=1000, height=1000)

inputPanel(
	   selectInput("gene", label = "GeneOfInterest",
		       choices= mixedsort(fD$symbol), selected=c("Krt18","Acta2","Csn2","Cd74")
,
		       multiple=TRUE, selectize=FALSE)
	  )

renderPlot({
    pD$cluster <- clustering()

    genes <- input$gene
	 plotGeneDist(m, pD, fD, genes, colorBy="cluster")
   }, width=800, height=800)

>>>>

rnd_seed <- 300
clustDat <- readRDS("../data/Robjects/secondRun_2500/ClusterComparison.rds") 
# bootDat <- readRDS("../data/Robjects/ClusterBootstrap.rds")
dataList <- readRDS("../data/Robjects/secondRun_2500/ExpressionList_QC_norm.rds")
# set.seed(rnd_seed)
# dataList <- subSample(dataList,cell.number=10000)

@@

# fD$keep <- rowMeans(m) > 0.01 & fD$keep

#Gene and Cell filtering
m <- m[fD$keep,pD$PassAll]
pD <- pD[pD$PassAll,]
fD <- fD[fD$keep,]

# only keep highVar
m <- m[fD$highVar,]
fD <- fD[fD$highVar,]
#Normalization
m <- t(t(m)/pD$sf)

@@

tsnPlot1 <- ggplot(pD, aes(x=tSNE1, y=tSNE2, color=Condition, shape=Replicate)) +
    geom_point(size=1) +
    theme_bw()
tsnPlot1

@@

#Visualize Dendrograms
clustering <- reactive({
    lbl <- paste(input$dm,input$lk,input$ds,sep="_")
    print(lbl)
    cluss <- unname(clustDat[[lbl]][["Labels"]])
})

@@

renderPlot({
    pD$cluster <- clustering()
    set.seed(rnd_seed)
    subsP <- group_by(pD, cluster) %>%
	do(sample_n(.,min(200,nrow(.)))) %>%
	arrange(cluster)

    nclust <- length(unique(pD$clust))

    # Compute smaller dis matrix
    trafM <- t(log2(m[,as.character(subsP$barcode)]+1))
    if(input$dm=="euclidean") {
	dis <- dist(trafM,method=input$dm)
    } else {
	dis <- as.dist((1-cor(t(trafM),method=input$dm))/2)
    }

    #traf to simmat
    simMat <- asSim(as.matrix(dis))
    simMat <- simMat[as.character(subsP$barcode), as.character(subsP$barcode)]

    #prep heatmap
    annoCol <- data.frame("cluster"=as.factor(subsP$cluster),
			  "Condition"=subsP$Condition)
    rownames(annoCol) <- as.character(subsP$barcode)
    ann_colors <- list("cluster"=rainbow(nclust))
    names(ann_colors$cluster) <- c(min(subsP$cluster):max(subsP$cluster))
    pheatmap(simMat,
	     cluster_rows=FALSE,
	     cluster_cols=FALSE,
	     show_rownames=FALSE,
	     show_colnames=FALSE,
	     annotation_col=annoCol,
	     annotation_colors=ann_colors)
}, width=1200, height=1200)
#

# ---- PCAonAvgExpression ----

renderPlot({
# Compute mean expression values
pD$cluster <- clustering()
nclust <- length(unique(pD$cluster))
out <- data.frame("C0"=numeric(nrow(m)))
for (clust in unique(pD$cluster)) {
    expr <- rowMeans(log2(as.matrix(m[,pD$cluster==clust])+1))
    colname <- paste0("C",clust)
    out[,colname] <- expr
}

# Compute euclidean distances
meandist <- dist(t(out))

# PCA
pc <- prcomp(t(out))

# Plot
palette(rainbow(nclust))
plot(pc$x[,1],pc$x[,2],col=c(1:10),pch=20,cex=2,xlab="PC1",ylab="PC2")
legend("topleft", legend = c(1:nclust), col = c(1:nclust), pch = 16)
})

renderPlot({
    pD$cluster <- clustering()
    genes <- c("Des","Sox17","Mcm3","Col3a1")
	 plotGeneDist(m, pD, fD, genes, colorBy="Condition")
   }, width=1000, height=1000)

inputPanel(
	   selectInput("gene", label = "GeneOfInterest",
		       choices= mixedsort(fD$symbol), selected=c(fD$symbol[1])
,
		       multiple=TRUE, selectize=FALSE)
	  )

renderPlot({
    pD$cluster <- clustering()
    genes <- input$gene
	 plotGeneDist(m, pD, fD, genes, colorBy="cluster")
   }, width=800, height=800)
